---
title: "Analysis of staffing levels for nursing and adult inpatient care"
author: "Mairead Bermingham"
date: "2023-08-10"
output: 
  powerpoint_presentation:
    reference_doc: HIS_PowerPoint_template.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Markdown Elements (1)
*italic*, **bold**, --strikeout--, ~subscript~, ^superscript^, [small caps]{.smallcaps}, `verbatim`

<br>

1. Ordered list item 1
2. Ordered list item 2

* Unordered list item 1
* Unordered list item 2


## Image
![Image 1 - A dog](https://images.unsplash.com/photo-1643644323421-7e1cfbb2f26d?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2070&q=80)

## Table
     species    sepal.length    sepal.width
------------    -------------   ------------
     setosa     5.1             3.5
  virginica     7.4             2.8
 versicolor     6.4             3.2

## Multi-column Layout
:::::::::::::: {.columns}
::: {.column}
This is the **first** column

- List item 1
- List item 2
:::
::: {.column}
And this is the *second* column

* Item
* Item
:::
::::::::::::::
## Elavator Pitch

Context Proble How we are gong to olve it

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


#Som EDAs

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Loading the libraries

```{r warning=FALSE, messages=FALSE}
library(tidyverse) 
```
### Meta
```{r}
glimpse(mtcars) 
```
## Some EDAs
**This is the most critical part**

```{r cor}
ggplot(mtcars)+
  geom_point(aes(x=mpg, y=hp))+
  theme_minimal()
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
